---
title: "Dominant Flows Analysis"
author: "Timothee Giraud"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dominant_Flows_Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## The method
Dominant Flows Analysis establishes a hierarchy between nodes.
Used in geography it shows the influence of the distance and barrier effects on 
regionalisation.  

## Data
Data used here are residential migrations between *communes* of the Lot *département* from 2003 to 2008. 

## How to use the package
First case :   
`i` is dominated by `j` when:  

* `i` sends its biggest flow to `j`  
* `j` receives more flows than `i`

```{r, fig.show='hold', fig.width = 7, fig.height=7}
library(flow)

data(lot)

dom1<- flowDom(mat = MRE46,
               i = "DCRAN",
               j = "CODGEO",
               fij = "NBFLUX_C08_POP05P")

head(dom1)

plotflowDom(fdom = dom1, spdf = COM46, id = "INSEE_COM")
title("Residential Dominant Flows")
```

Second case :   
`i` is dominated by `j` when:    

* `i` sends at least 50 % of its flows to `j`   
* `j` receives more flows than `i`

```{r, fig.show='hold', fig.width = 7, fig.height=7}

dom2 <- flowDom(mat = MRE46,
                i = "DCRAN",
                j = "CODGEO",
                fij = "NBFLUX_C08_POP05P",
                k = 0.5)

plotflowDom(fdom = dom2, spdf = COM46, id = "INSEE_COM")
title("Residential Dominant Flows (50% flows threshold)")
```

It is possible to add the names of dominant centers :

```{r, fig.show='hold', fig.width = 7, fig.height=7}

plotflowDom(fdom = dom2, spdf = COM46, id = "INSEE_COM", name = "NOM_COM")
title("Residential Dominant Flows (50% flows threshold)")
```




